cardinalR: Generating interesting high-dimensional data structures

### 2025-09-16 paper-cardinalR.Rmd
Updated pyramid table info

```{r}
pyramid_tb <- tibble(fun = c("gen_pyrrect",
                             "gen_pyrtri",
                             "gen_pyrstar",
                             "gen_pyrholes"), 
                        exp = c("Generate a pyramid with a rectangular base, with the option of a sharp or blunted apex.",
                                "Generate a pyramid with a triangular base, with the option of a sharp or blunted apex.",
                                "Generate a pyramid with a star-shape base, with the option of a sharp or blunted apex.",
                                "Generate a pyramid with triangular pyramid shaped holes."))
```

>>>>

```{r}
pyramid_tb <- tibble(fun = c("gen_pyrrect",
                             "gen_pyrtri",
                             "gen_pyrstar",
                             "gen_pyrholes"), 
                        exp = c("Rectangular-base pyramid, with a sharp or blunted apex.",
          "Triangular-base pyramid, with a sharp or blunted apex.",
          "Star-shaped base pyramid, with a sharp or blunted apex.",
          "Pyramid containing triangular pyramid-shaped holes."))
```

### 2025-09-16 paper-cardinalR.tex
Updated pyramid table info

\caption{\label{tab:pyramid-tb-pdf}cardinalR pyramid data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_pyrrect & Generate a pyramid with a rectangular base, with the option of a sharp or blunted apex.\\
gen\_pyrtri & Generate a pyramid with a triangular base, with the option of a sharp or blunted apex.\\
gen\_pyrstar & Generate a pyramid with a star-shape base, with the option of a sharp or blunted apex.\\
gen\_pyrholes & Generate a pyramid with triangular pyramid shaped holes.\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:pyramid-tb-pdf}cardinalR pyramid data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_pyrrect & Rectangular-base pyramid, with a sharp or blunted apex.\\
gen\_pyrtri & Triangular-base pyramid, with a sharp or blunted apex.\\
gen\_pyrstar & Star-shaped base pyramid, with a sharp or blunted apex.\\
gen\_pyrholes & Pyramid containing triangular pyramid-shaped holes.\\
\bottomrule
\end{tabular}
\end{table}
